EVALUATING MODEL PREDICTIVE CONTROL IN DIFFERENTIAL DRIVE ROBOTICS: \\ COMPREHENSIVE LITERATURE REVIEW

### 2024-09-19 src/amr_control/docs/paper.tex
Kein erfolg

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{fancyhdr}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{subcaption}
\usepackage{blindtext}
\usepackage{microtype}
\usepackage{booktabs}
\usepackage{caption}
\usepackage[numbers,sort&compress]{natbib}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em

@@

@@

% Paper contribution
This work addresses these challenges by developing a nonlinear Model Predictive Controller (nMPC) for differential drive mobile robots, specifically designed for dynamic obstacle avoidance. The primary contribution is the integration of nMPC to improve real-time navigation performance in dynamic environments. Unlike conventional approaches such as DWA, the proposed nMPC effectively handles nonlinear dynamics and dynamic obstacles, offering superior prediction accuracy and responsiveness.

@@

\bibliographystyle{IEEEtran}
\bibliography{references}

@@

>>>>

\documentclass[conference]{IEEEtran}

\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{fancyhdr}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{subcaption}
\usepackage{blindtext}
\usepackage{microtype}
\usepackage{booktabs}
\usepackage{caption}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{algorithm}
\usepackage{algpseudocode}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em

@@

\cite{ASAP}

\ref{fig:DWA_TEB_MPC_ASAP_path}

\begin{figure}[!h]
    \centering
    \includegraphics[width=1\columnwidth]{images/DWA_TEB_MPC_ASAP_path.png}
    \caption{Blockdiagram of nMPC for future Implementation }
    \label{fig:DWA_TEB_MPC_ASAP_path}
\end{figure}

\begin{figure}[!h]
    \centering
    \includegraphics[width=1\columnwidth]{images/DWA_TEB_MPC_ASAP_stats.png}
    \caption{Blockdiagram of nMPC for future Implementation }
    \label{fig:DWA_TEB_MPC_ASAP_stats}
\end{figure}

@@

% Paper contribution
This work contributes to the state-of-the-art development, of a nonlinear Model Predictive Controller for a mobile robot with integrated dynamic obstacle avoidance.

The main objective is to design a local planner that effectively addresses the challenges of dynamic obstacle avoidance, offering improved performance in real-time navigation within dynamic environments.

This work addresses these challenges by developing a nonlinear Model Predictive Controller (nMPC) for differential drive mobile robots, specifically designed for dynamic obstacle avoidance. The primary contribution is the integration of nMPC to improve real-time navigation performance in dynamic environments. Unlike conventional approaches such as DWA, the proposed nMPC effectively handles nonlinear dynamics and dynamic obstacles, offering superior prediction accuracy and responsiveness.

@@

@@

\subsection{Reference Trajectory}
